In the least-square method the optimal values of parameters providing the best agreement between theoretical predictions and data are estimated by minimising the difference between the measurements and calculations. Given theoretical predictions, $t_i\left( \mathbf{a} \right)$, for the cross section bin $i$ which depend on the vector of parameters of interest $\mathbf{a}$, the outcome of the measurement, $m_i$, can be modelled as follows~\cite{Stump:2001gu,Botje:2001fx}:
\begin{equation}
 m_i = t_i\left( \mathbf{a} \right) + \varepsilon_{i} \sigma_{i,\text{uncor}} + \sum_{\mu=1}^{K}{b_{i,\mu}\sigma_{i,\text{cor}}^\mu}, \qquad i=1\ldots N_\text{bins},
\end{equation}
where $\sigma_{i,\text{uncor}}$ is an estimate of total uncorrelated uncertainty for the cross section measurement and $\varepsilon_{i}$ is a random normally distributed variable with mean value $\left\langle \varepsilon_{i}\right\rangle = 0$ and variance $\text{Var}\left( \varepsilon_{i}\right) = 1$; $\sigma_{i,\text{cor}}^\mu$ and $b_{i,\mu}$ represent the correlated uncertainty from source $\mu$ and the corresponding systematic shift, respectively. It is assumed that the systematic shifts can also be modelled by normally distributed random variables with zero mean and unit variance. In order to take into account proportionality of the systematic uncertainties to the central value\footnote{Most of the systematic uncertainties in this analysis e.g. absolute normalisation uncertainty or acceptance correction uncertainty to good approximation are proportional to the central value of the measured cross section.}, the corresponding uncertainty components are expressed as $\sigma_{i,\text{cor}}^\mu = \gamma_{i,\mu}t_i$, where 
\begin{equation}
\gamma_{i,\mu}=\frac{1}{{m_i}} \frac{\partial m_i}{\partial b_{i,\mu}}
\end{equation}
is the relative correlated systematic uncertainty quantifying the sensitivity of the measurement $i$ to the systematic source $\mu$. The statistical uncertainty is assumed to scale proportionally to the square root of expected number of events. Corrected for bias from systematic shifts, the statistical uncertainty is equal to
\begin{equation}
 \sigma_{\text{stat},i} = \delta_{\text{stat},i}\cdot m_i\left( t_i - \sum_\mu\gamma_{i,\mu}t_ib_\mu \right),
\end{equation}
where $\delta_{\text{stat},i}$ is the relative statistical uncertainty. The difference between data and theoretical predictions is evaluated using the weighted squared norm, thus the so-called $\chi^2$-function used in the QCD fit  for statistically uncorrelated measurements is defined as:
\begin{equation}
 \chi^2 = \sum_i{ \frac{\left( m_i-t_i-\sum_{\mu}{\gamma_{i,\mu} t_i b_\mu} \right)^2 }{ \delta_{\text{stat},i}^2\left( t_i - \sum_\mu{\gamma_{i,\mu}t_ib_\mu} \right)m_i + \left( \delta_{i,\text{uncor}}t_i\right)^2 } } + \sum_{\mu}{b_\mu^2},
 \label{eq:chi2uncorr}
\end{equation}
with $\delta_{i,\text{uncor}}$ --- relative uncorrelated systematic uncertainty. The last term in this equation represents the penalty for the systematic-shift parameters. In order to take into account statistical correlations between different data points the $\chi^2$-function can be re-expressed as follows~\cite{Aaron:2009aa}:
%\begin{equation}
% \chi^2\left( \mathbf{m},\mathbf{b}\right) = \sum_{i}{\frac{\left[ m^i-\Sigma_j{\gamma^i_jm^ib_j-\mu^i}\right]^2 }{\left( \delta_{i,\text{stat}}\mu^i\right)^2 + \left( \delta_{i,\text{uncor}}\mu^i\right)^2 }} + \sum_{j}{b_j^2}
% \label{eq:chi2uncor}
%\end{equation}
\begin{align}
 \chi^2 &= \sum_{ij}{\left( m^i -\sum_{\mu}{\Gamma_\mu^i\,b_\mu - t^i }\right) C^{-1}_{ij} \left( m^j -\sum_{\mu}{\Gamma_\mu^j\,b_\mu - t^j }\right) }\notag\\
                                           &+ \sum_{\mu}{b_\mu^2},
 \label{eq:chi2corr}
\end{align}
where the $C_{ij}$ is covariance matrix for the measured data points. It is equal to the sum of covariance matrices for statistical and uncorrelated systematic uncertainty components\footnote{The covariance matrix for uncorrelated uncertainties has diagonal form.} $C_{ij}=C_{ij}\left(t_i\right)=C_{ij}^{\text{stat.}}+C_{ij}^{\text{uncor.}}$. The $\Gamma_\mu^l$ is related to the relative correlated systematic uncertainties
\begin{equation}
 \Gamma_{\mu}^i = \gamma_{\mu}^i \cdot t^i. 
\end{equation}

As it was mentioned, some systematic variations in this analysis resulted in asymmetric change of the cross section values, thefore some measurement bins have asymmetric uncertainties. In order to conform with the definition of the $\chi^2$-function, the asymmetric uncertainlies are converted into symmetric form according to:
\begin{equation}
 \sigma_i^{sym} = \frac{\sigma_i^+ + \sigma_i^-}{2},
\end{equation}
with $\sigma_i^{+\left(-\right)}$ expressing positive (negative) component of asymmetric uncertainty.

The determination procedure of the parameters that best fit the data is based on the numerical minimisation of the $\chi^2$ function with respect to free parameters. The systematic shifts $\mathbf{b}$, described above, are fitted simultaneously with physical parameters in order to take into account the correlation of systematic uncertainties across measurement points.

The quality of the fit is assessed by the value of $\chi^2$-function in its minimum. Assuming that the measurements are normally distributed around the expectation value provided by theoretical predictions and with the variance described by the covariance matrix, the $\chi^2$ value can be treated as a random variable with the mean value equal to the number of degrees of freedom $\left\langle \chi^2 \right\rangle = n_\text{DF}$, which in case of $n_\text{par}$ parameter fit to $n_\text{p}$ points is $n_\text{DF}=n_\text{p}-n_\text{par}$\footnote{Due to penalty term, the nuisance parameters $\mathbf{b}$ are not free parametes, hence they do not contribute to the number of degrees of freedom.}. Therefore, the ratio
\begin{equation}
 \chi^2/n_\text{DF} \approx 1
\end{equation}
is an indication of the good quality of the fit.

\textcolor{blue}{These setting define the, so-called ``central-fit''. The value of the strong coupling determined with this setup is used as a reference for the studies of the sensitivity of the extracted \asz to the variation of the theory parameters that will be discussed in a section devoted to the treatment of systematic uncertainties (see Section~\ref{subsec:assystematics}).}
