The detailed description of systematic uncertainties on the measured jet cross sections was presented in Chapter~\ref{ch:resultscs}. The uncertainties attributed to the inclusive DIS measurements are summarised in~\cite{Aaron:2009aa}. Besides experimental uncertainties on the measured values, additional sources appear due to that of external input used in theoretical predictions. In general, the absolute magnitude of the uncertainties on the cross-section values must be accompanied by information about mutual correlations between the measured values in different cross-section bins. The correlations are taken into account in the $\chi^2$, as described above (see Eq.~\ref{eq:chi2corr}). Sometimes, an estimate of the correlation of systematic uncertainties is not known because the evaluation procedure can be very difficult or even does not exist. %For example, no commonly accepted prescription for the estimation of bin-to-bin correlations attributed to the truncation of the perturbative series exist. 
However, information about correlations is important and some assumptions have to be made\footnote{The following simple example can be considered. In general, the least-squares method for the problem with single fit-parameter e.g.~\asz, can be interpreted as a weighted averaging of \asz values extracted from individual cross-section bins with weights that are inversely proportional to the squared experimental uncertainty. Assume the luminosity is the only source of systematic uncertainty. The relative error due to luminosity is equal for all bins, thus, if treated as uncorrelated, the resulting uncertainty $\Delta\asz$ scales $\propto 1/\sqrt{\text{N}_\text{bins}}$, because there are $\text{N}_\text{bins}$ independent \asz measurements. However, in the case of a fully correlated treatment, $\Delta\asz$ will not improve when extra measurements are included, because the cross sections are assumed to shift up or down in all bins simultaneously. Obviously, for this example, the fully correlated treatment is the correct one.}. Fortunately, positive statistical correlations in inclusive-jet measurements emerging due to the fact that more than one jet can appear in the same event, are relatively easy to assess. In such a case the correlations are represented by the statistical covariance matrix $C_{ij}^{\text{stat.}}$ that was described in Section~\ref{subsec:statcorel}. In general, positive correlations between individual measurements result in larger uncertainty when propagated to the fit parameters. The treatment of individual systematic sources is summarised below and is motivated by the following argument: 
\begin{itemize}
 \item \textbf{correlated systematic sources:}
 \begin{itemize}
 \item the uncertainty on the cross-section normalisation due to the luminosity measurement $\delta_\text{lumi}$ is fully correlated across all measurement points because according to Eq.~\eqref{eq:csdef} the integrated luminosity $\mathcal{L}$ enters the cross section as a constant common factor for all measurements;
 \item the absolute jet-energy scale uncertainty $\delta_\text{JES}$ is treated as fully correlated. This error accounts for the precision of the jet-energy calibration. The calibration constants were determined as functions of the jet pseudorapidity in the laboratory frame. It is assumed that the extracted values deviate from the true ones in a correlated manner, because the jet-calibration technique may have a common bias for all bins.
 \item the model uncertainty was treated as correlated. Such an approach is supported by the observation that the individual systematic variations performed for this source (see Section~\ref{sec:mcvalidation}) result in correlated deviations of the extracted cross sections with respect to the central value;
 %\item the absolute jet-energy scale uncertainty $\delta_\text{JES}$ is treated as fully correlated. This error accounts for the precision of the jet-energy calibration. The calibration constants were determined as functions of the jet pseudorapidity in the laboratory frame. It is assumed that the extracted values deviate from the true ones in a correlated manner.
 \end{itemize}
 \item \textbf{uncorrelated systematic sources:}
 \begin{itemize}
 \item the normalisation uncertainty due to the simulation of the track-veto efficiency in MC, $\delta_\text{TV}$, was treated as uncorrelated by the same argument;
 \item conceptually, the uncertainty due to the absolute electron-energy scale $\delta_\text{EES}$ has to be treated in the same way as the jet-energy scale error. However, as demonstrated in Section~\ref{subsec:systunc} the contribution of $\delta_\text{EES}$ to the total experimental uncertainty is typically below 1\%, and the effect of correlations can be neglected. Therefore, the $\delta_\text{EES}$ contribution was treated as uncorrelated for simplicity;
 \item the uncertainty due to electron identification $\delta_\text{eID}$ and due to the $\left(E-p_Z\right)$-cut variation $\delta_\text{E-Pz}$ were also assumed to be uncorrelated.
 \end{itemize}
\end{itemize}
The uncertainties from uncorrelated sources except for statistical errors were added in quadrature and included as a single uncorrelated source in the $\chi^2$-function. The fit uncertainties of \asz, resulting from the experimental uncertainties, were determined by means of the ``Hesse'' method\footnote{A detailed discussion of the ``Hesse'' approach can be found in~\cite{Cooper:2010}.} implemented in \minuit~\cite{James:1975dr}. A study of the effect of experimental precision of the data on \asz extraction is summarised in Section~\ref{subsec:asexpunc}.
\begin{table}[t]
\centering
\begin{tabular}{|l|c|c|}
\hline
 systematic source & correlated & uncorrelated \\
\hline
\multicolumn{3}{c}{experimental}\\
\hline
 luminosity & $\times$ & \\
 jet energy scale & $\times$ & \\
 MC model & $\times$ &  \\
\hline
 electron energy scale & & $\times$  \\
 electron identification & & $\times$ \\
 track-veto reweighting & & $\times$ \\
 $\left(E-p_Z\right)$-cut & & $\times$ \\
\hline
\multicolumn{3}{c}{theoretical}\\
\hline
 renormalisation scale & $\times$ & \\
 factorisation scale & $\times$ & \\
 hadronisation corrections & & $\times$ \\
\hline
\hline
\asz assumed in pPDF & \multicolumn{2}{|c|}{\asz=0.1184$\pm$0.0007~\cite{Bethke:2012jm}} \\
parton density function & \multicolumn{2}{|c|}{PDF error analysis} \\
\hline
\end{tabular}
\caption{Splitting of the systematic uncertainty sources into correlated and uncorrelated components.}
\label{tab:correlsyst} 
\end{table}

Besides experimental uncertainties, the stability of the fit with respect to theoretical assumptions has to be investigated. In this analysis, theoretical uncertainties related to the variation of renormalisation and factorisation scales were treated as correlated. A detailed discussion of the effect of different approaches for the treatment of scale variations is presented in Section~\ref{subsec:asscalevar} together with a discussion of the sensitivity of the fit, procedure to PDF parametrisation and implicit \asz assumptions. Table~\ref{tab:correlsyst} contains an outline of the systematic uncertainty treatment.