\thispagestyle{empty}
\begin{center}
\huge\textbf{Acknowledgement}
\end{center}

This work would be impossible without contribution of numerous people to which I am deeply indebted. 

I would like to express my gratitude to supervisors \textbf{Prof. Dr. Brian Foster} and \textbf{PD Dr. Olaf Behnke} for their dedication to this analysis and kind support during the tough moments. I am especially pleased to thank them for the critical review of the thesis manuscript and numerous indispensable suggestions. 

I thank \textbf{Prof. Dr. Erika Garutti} and \textbf{\sl{Prof. Dr. Caren Hagner}}, \textbf{Prof. Dr. Sven-Olaf Moch} and  \textbf{Dr. Thomas Sch\"{o}rner-Sadenis} for agreeing to be the members of the examination committee.

I wish to express my appreciation to \textbf{Dr. Daniel Britzger}, \textbf{Dr. Ringaile Pla\v{c}akyt\.{e}}, \textbf{Dr. Voica Radescu} and \textbf{Dr. Katarzyna Wichmann} for helping to resolve various technical issues experienced within the course of my studies with \fastnlo and \herafitter. Additionaly, I express the utmost appreciation to my officemate \textbf{Inna Makarenko}. This thesis significantly owes its existence to the close collaboration with you.

I would like to thank \textbf{Dr. Ingrid-Maria Gregor} for inviting me to \desy pixel telescope group. I am grateful to \textbf{Dr. Claus Kleinwort}, \textbf{Dr. Rainer Mankel}, \textbf{Dr. Hanno Perrey} and \textbf{Dr. Igor Rubinskiy} for their help and encouragement during my involvement in the \eutelescope project.

I cordially thank to my first teachers \textbf{Dr. Volodymyr Aushev}, who provided the possibility to join the world-class research at \desy, as well as \textbf{Prof. Dr. Cluadia Glasman} and \textbf{Prof. Dr. Juan Terron}, who introduced me to the exciting area of jet physics. Besides being ..

The importance of the feedback from other researchers from the \zeus collaboration cannot be overestimated. I thank all in the \textbf{\zeus group} who expressed interest in this analysis.

The research would not be such an interesting endeavour without friends, therefore I am pleased to express my warmest acknowledgement to all former colleagues from the \textbf{\zeus-Kyiv group}. It was great to share happy moments with you.

Finally, my wholehearted gratitude goes to loving family and especially to my dear wife for their unconditional love, patience and support.