All microscopic phenomena observed to date can be described in the framework of the Standard Model (SM). The SM is a renormalisable quantum field theory of the strong, electromagnetic and weak interactions. According to the SM, the matter particles are represented by spin-$\frac{1}{2}$ Dirac fermions coming in three generations while interaction between matter fields is mediated by spin-1 gauge bosons. The SM is based on combined local $\mathrm{SU}\left(3\right) \bigotimes \mathrm{SU}\left(2\right)_{L} \bigotimes \mathrm{U}\left(1\right)$ symmetry representing strong, weak and electromagnetic sectors, respectively. The fermions are distinguished by the quantum numbers corresponding to the gauge groups. Quark fields are endowed with electroweak and colour charges, while leptons (electron $e$, muon $\mu$, tau $\tau$ and three corresponding neutrinos $\nu_e, \nu_\mu, \nu_\tau$) carry only electroweak charge. As a consequence of exact local gauge symmetry, the mediators of the strong force, gluons, are massless quanta. In contrast to the strong interaction, three electroweak gauge bosons $W^\pm, Z^0$ acquire mass as a result of spontaneous $\mathrm{SU}\left(2\right) \bigotimes \mathrm{U}\left(1\right)$ symmetry breaking, while the photon $\gamma$ stays massless. According to the Higgs mechanism, elementary particles acquire mass due to coupling to the scalar field, quanta of which have been recently discovered at the LHC~\cite{pl:b716:1,pl:b716:30}.

\textcolor{blue}{?Need some transition words here. Something like:} In this interpretation of the data work is based on the Standard Model picture of particle physics. Subsequent sections briefly outline the theoretical framework used for the description of the strong sector of the Standard Model and hard interactions at \hera in particular.

\section{Kinematics of DIS}
\label{sec:kindis}
\input{parts//PartI_Analysis//theory//kinematics}

\subsection{Breit Frame}
\label{subsec:breitframe}
\input{parts//PartI_Analysis//theory//breitframe}

\subsection{Jet Production in the Breit frame}
\label{subsec:jetsinbreit}
\input{parts//PartI_Analysis//theory//jetsinbreit}

\section{Quantum Chromodynamics}
\input{parts//PartI_Analysis//theory//generalqcd}

\section{Structure of Perturbative Calculations}
\input{parts//PartI_Analysis//theory//perturbation}

\subsection{Renormalisation and Renormalisation Group Equation}
\input{parts//PartI_Analysis//theory//rge}

\section{Factorisation}
\input{parts//PartI_Analysis//theory//factorisation}

\section{DGLAP Equations}
\input{parts//PartI_Analysis//theory//dglap}

\subsection{Scale choice}
\input{parts//PartI_Analysis//theory//scalechoice}

\section{Next-to-Leading-Order Jet Cross-Section Calculation}
\input{parts//PartI_Analysis//theory//nlojetcscalc}

\subsection{Subtraction scheme}
\label{subsec:subscheme}
\input{parts//PartI_Analysis//theory//subscheme}
 
\subsection{Jet Algorithms}
\label{subsec:jetalgo}
\input{parts//PartI_Analysis//theory//jetalgo}
%\subsection{Global fits}
%\input{parts//PartI_Analysis//theory//globalfits}

\section{Monte Carlo models and Jet Production}
\input{parts//PartI_Analysis//theory//mcmodels}